### 2019-02-21 paper/intro-notes.tex
Update spacing and DSR lit

India is a particularly compelling case.
India has long shown a strong preference for boys, especially in the northern 
states \citep{Kishor1993,murthi95,arnold98}.%
\footnote{
The proportion of couples who ideally wants more boys than girls does, however,
appear to be decreasing over time and with higher education \citep{bhat03,pande07}.
}
As a result, mortality risk is higher for females than males, leading to an almost
continuous increase in India's overall ratio of males to females over the last century 
\citep{dyson01,Navaneetham2011,Bongaarts2015}.
India has also seen dramatic increases in the males-to-females ratio  
at birth over the last three decades as access to prenatal sex determination 
expanded \citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2012}.
In addition, fertility has declined substantially, to the point where it is now
at, or even below, replacement in some areas 
\citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
This decline in fertility, combined with the strong preference for sons, has lead to an 
intensified pressure to use sex selection \citet{Guilmoto2009a,Jayachandran2017}.%
\footnote{
In some instances, however, the fertility decline appears to have created a stronger 
aversion to daughters rather than a stronger preference for son \citet{DiamondSmith2008}.
}

@@

>>>>

India is a particularly compelling case.
India has long shown a strong preference for boys, especially in the northern 
states \citep{Kishor1993,murthi95,arnold98}.%
\footnote{
The proportion of couples who ideally wants more boys than girls does, however,
appear to be decreasing over time and with higher education \citep{bhat03,pande07}.
}
As a result, mortality risk is higher for females than males, leading to an almost
continuous increase in India's overall ratio of males to females over the last century 
\citep{dyson01,Navaneetham2011,Bongaarts2015}.
India has also seen dramatic increases in the males-to-females ratio  
at birth over the last three decades as access to prenatal sex determination 
expanded \citep{das_gupta97,Sudha1999,Arnold2002,retherford03b,jha06,Guilmoto2012}.
In addition, fertility has declined substantially, to the point where it is now
at, or even below, replacement in some areas 
\citep{Guilmoto2013,Dharmalingam2014,International-Institute-for-Population-Sciences-IIPS2017}.
This decline in fertility, combined with the strong preference for sons, has lead to an 
intensified pressure to use sex selection \citet{Guilmoto2009a,Bongaarts2013,Jayachandran2017}.%
\footnote{
In some instances, however, the fertility decline appears to have created a stronger 
aversion to daughters rather than a stronger preference for son \citet{DiamondSmith2008}.
}

@@

Parents are also more likely to cease childbearing after the birth of 
a son than after a daughter 
\citep{repetto72,ben-porath76b,Das1987,Arnold1997,arnold98,clark00,dreze01,filmer09,Basu2010,Altindag2016}.
}
